Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-03-09 manuscript.Rmd
added ages to TSK and MFM; provided by Brauer and Franscesco

\newpage
<!-- READ DATA -->
```{r}
if (file.exists(here("data","output","DAL_spectra.rds"))) {
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data("DAL")
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
}

if (file.exists(here("data","output","MFM_spectra.rds"))) {
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data("MFM")
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
}

if (file.exists(here("data","output","TSK_spectra.rds"))) {
  TSK = readRDS(here("data","output","TSK_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data("TSK")
  TSK = readRDS(here("data","output","TSK_spectra.rds"))
}
```

>>>>

\newpage
<!-- READ DATA -->
```{r}
source(here("R","ages.R"))
if (file.exists(here("data","output","DAL_spectra.rds"))) {
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data("DAL")
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
}

if (file.exists(here("data","output","MFM_spectra.rds"))) {
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
  MFM[MFM$depth=="A4UR_72-74", 'depth'] = "A5UR_72-74" #fixing typo in sample name
  MFM$age = fn_age(MFM$depth)
} else {
  source(here("R","read_data.R"))
  read_data("MFM")
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
}

if (file.exists(here("data","output","TSK_spectra.rds"))) {
  TSK = readRDS(here("data","output","TSK_spectra.rds"))
  TSK$age = fn_age(TSK$depth)
} else {
  source(here("R","read_data.R"))
  read_data("TSK")
  TSK = readRDS(here("data","output","TSK_spectra.rds"))
}
```
